Xolotl: An Intuitive and Approachable Neuron \& Network Simulator in MATLAB

### 2018-06-08 paper/paper.tex
started work on figure_network

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%		BENCHMARKS
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%		DISCUSSION
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We envision that "xolotl" will be helpful in teaching students how to interpret cellular biophysics. The modular structure of "cpplab" and the graphical interface simplifies the process of manipulating and analyzing the properties of electrical excitability.

\subsection{Reproducibility}

@@

\subsection{Applications of \texttt{cpplab}}

@@

SG-S & AH designed and wrote the software, and wrote the manuscript. AH created the online user documentation. EM supervised the project. All authors reviewed the paper.

>>>>

- failure of averaging
- complex interrelationships b/w parameters and dynamics
- not clear what parameter does what
- traditional approach: vary parameters, but for more than 2 D, how do you even visualize this? also slow. expensive to set up. 
- need something where parameter variation can be linked to dynamics, easy to set up, easy to use.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%		BENCHMARKS
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%		DISCUSSION
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We set out to design a neuron and network simulator that could be useful in the classroom setting, especially for students of computational students, while also being powerful, fast and extensible enough to be used for research. By using a novel architecture that .., we showed how to create and simulate (1) single-compartment models of Hogkin-Huxley like neurons (Figure \ref{fig:figurehh}), (2) voltage clamp experiments and recover activation functions of single channel types (Figure 2), (3) a network of neurons with multiple synapse types (Figure 3), (4) a multi-compartment neuron model where the voltage of every compartment is coupled, and (5) a neuron model where homeostatic mechanisms control the maximal conductance of multiple channel types.

\subsection{Software use and reproducibility of research}

- reproducibility crisis in computational science 
- multiple sources: software being used is closed-source, researcher's code is not made available; obscure architecture makes improper use possible. 
- how xolotl conributes to reoridubile science: (1) freely available, code for this paper available too for others to inspect and replicate (2) intutitive syntax, solid documentation. (3) architectural choices that ensure accountability: object hashing, parameter hashing possible.

@@

\subsection{Applications of the \texttt{cpplab} architecture}

@@

SG-S \& AH designed and wrote the software, and wrote the manuscript. AH created the online user documentation. EM supervised the project. All authors reviewed the paper.
